%% First Schedule - The States
\DeclareSchedule{I}{states}
\Schedule{FIRST}{THE STATES}{%
    \section*{I. THE STATES}
    
    \begin{longtable}{p{0.1\textwidth}p{0.4\textwidth}p{0.4\textwidth}}
    \toprule
    \textbf{No.} & \textbf{Name} & \textbf{Territories} \\
    \midrule
    \endhead
    
    1. & Andhra Pradesh & The territories specified in sub-section (1) of section 3 of the Andhra Pradesh Reorganisation Act, 2014. \\
    
    2. & \Substituted{Assam}{Assam}{Constitution (One Hundred and First Amendment) Act, 2016, s. 15 \wef{16-9-2016}} & The territories which immediately before the commencement of this Constitution were comprised in the Province of Assam, the Khasi States and the Assam Tribal Areas. \\
    
    3. & Bihar & The territories which immediately before the commencement of this Constitution were comprised in the Province of Bihar. \\
    
    4. & Gujarat & The territories specified in sub-section (1) of section 3 of the Bombay Reorganisation Act, 1960. \\
    
    5. & Haryana & The territories specified in sub-section (1) of section 3 of the Punjab Reorganisation Act, 1966. \\
    
    6. & Himachal Pradesh & The territories specified in sub-section (1) of section 3 of the State of Himachal Pradesh Act, 1970. \\
    
    7. & \Inserted{Jharkhand}{Constitution (Eighty-eighth Amendment) Act, 2003, s. 2 \wef{15-11-2000}} & \Inserted{The territories specified in sub-section (1) of section 3 of the Bihar Reorganisation Act, 2000.}{Constitution (Eighty-eighth Amendment) Act, 2003, s. 2 \wef{15-11-2000}} \\
    
    8. & Karnataka & The territories specified in sub-section (1) of section 3 of the States Reorganisation Act, 1956. \\
    
    9. & Kerala & The territories specified in sub-section (1) of section 5 of the States Reorganisation Act, 1956. \\
    
    10. & Madhya Pradesh & The territories specified in sub-section (1) of section 9 of the States Reorganisation Act, 1956. \\
    
    \bottomrule
    \end{longtable}
    
    \section*{II. THE UNION TERRITORIES}
    
    \begin{longtable}{p{0.1\textwidth}p{0.4\textwidth}p{0.4\textwidth}}
    \toprule
    \textbf{No.} & \textbf{Name} & \textbf{Territories} \\
    \midrule
    \endhead
    
    1. & \Substituted{Andaman and Nicobar Islands}{Andaman and Nicobar Islands}{Constitution (One Hundred and First Amendment) Act, 2016, s. 15 \wef{16-9-2016}} & The territory which immediately before the commencement of this Constitution was known as the Andaman and Nicobar Islands. \\
    
    2. & Chandigarh & The territory specified in section 4 of the Punjab Reorganisation Act, 1966. \\
    
    3. & \Inserted{Dadra and Nagar Haveli and Daman and Diu}{Dadra and Nagar Haveli and Daman and Diu (Merger of Union Territories) Act, 2019, s. 3 \wef{26-1-2020}} & \Inserted{The territories which immediately before the commencement of the Dadra and Nagar Haveli and Daman and Diu (Merger of Union Territories) Act, 2019 were the Union territories of Dadra and Nagar Haveli and Daman and Diu.}{Dadra and Nagar Haveli and Daman and Diu (Merger of Union Territories) Act, 2019, s. 3 \wef{26-1-2020}} \\
    
    4. & Delhi & The territory which immediately before the commencement of this Constitution was comprised in the Chief Commissioner's Province of Delhi. \\
    
    5. & \Inserted{Jammu and Kashmir}{Constitution (One Hundred and Third Amendment) Act, 2019, s. 2 \wef{31-10-2019}} & \Inserted{The territory which, immediately before the commencement of the Constitution (Application to Jammu and Kashmir) Order, 2019, was included in the State of Jammu and Kashmir but excluding the territories specified in the Second Schedule to the Jammu and Kashmir Reorganisation Act, 2019.}{Constitution (One Hundred and Third Amendment) Act, 2019, s. 2 \wef{31-10-2019}} \\
    
    6. & \Inserted{Ladakh}{Constitution (One Hundred and Third Amendment) Act, 2019, s. 2 \wef{31-10-2019}} & \Inserted{The territories specified in the Second Schedule to the Jammu and Kashmir Reorganisation Act, 2019.}{Constitution (One Hundred and Third Amendment) Act, 2019, s. 2 \wef{31-10-2019}} \\
    
    7. & Lakshadweep & The territory specified in section 6 of the States Reorganisation Act, 1956. \\
    
    8. & Puducherry & The territories which immediately before the commencement of the Constitution (Fourteenth Amendment) Act, 1962, were comprised in the Union territory of Pondicherry. \\
    
    \bottomrule
    \end{longtable}
}